%-------------------------
% Resume in Latex
% Author : Kunal Kumar Jha
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{simplecv}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Kunal Kumar Jha} \\ \vspace{1pt}
    Full Stack Web Developer | Automation | Graphical Designer   \\ \vspace{1pt}
    \href{mailto:kunatastic@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{kunatastic@gmail.com}} ~ 
    \href{https://kunatastic.com}{\raisebox{-0.2\height}\faLink\ \underline{https://kunatastic.com}} ~ 
    \href{https://linkedin.com/in/kunatastic/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedIn/kunatastic}}  ~
    \href{https://github.com/kunatatsic}{\raisebox{-0.2\height}\faGithub\ \underline{github/kunatastic}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology}{June 2019 -- Present}
      {B. Tech in Computer Science and Engineering, CGPA: 9.17/10 \emph{(till 6th sem)}}{Chennai, IN}
%   \resumeSubHeadingListEnd
%   \vspace{-4pt}
%   \resumeSubHeadingListStart
    \resumeSubheading
      {Sri Pratibha Junior College}{April. 2017 -- May 2019}
      {Senior Secondary, Score: $$96.5\%$$}{Hyderabad, IN}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {PupilFirst (AICTC recognised)}{May 2022 -- Present}
      {Full Stack Developer Intern and Open Source Contributors}{Remote}
      \resumeItemListStart
        \resumeItem{Optimised the User Interface for smaller and medium display size devices and improved Lighthouse scores for responsiveness}
        \resumeItem{Developed a service to cancel the a set of unit tasks daily on a product in development in order to decrease time needed for team members to identify and fix bugs/issues.}
        \resumeItem{Explored ways to visualize and analysis to read the data from photos of a 5 para monitors in the ICU centers all across India.}
      \resumeItemListEnd

    \resumeSubheading
      {Procial Network}{July 2021 -- November 2021}
      {Full Stack Web Developer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Presented and implemented suggestions requested from real world stack holders along with 2 other interns and one of the top performing intern.}
        \resumeItem{Implemented browser based push notification framework in node.js and integration with present react application using service workers.}
        \resumeItem{Integrated global state management like redux with thunk to manage the data retrieved by the APIs.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Spark Foundation}{February 2021 -- March 2021}
      {Web Developer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Developed a 3rd party payment gateway full stack Application using React.js, Node.js, MongoDb and Express. that integrated RazorPay as the payment gateway for collecting donation for the charity.}
        \resumeItem{Customized automated email, designed and developed a lightweight, interactive user interface using Three.js.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
    \resumeProjectHeading
        {\textbf{Oxy-cure} $|$ \emph{React, Node.js, MongoDB, LeafLet}}{April 2021 -- May 2021}
            \resumeItemListStart
            \resumeItem{Developed an oxygen management system on visualised on maps for easy querying and easy accessibility.}
            \resumeItem{Implemented secure http-only cookie based JWT authentication to avoid any XXS or cookie hijacking attacks as user's location was very sensitive information.}
            \resumeItem{Processed the user's location data for easy retrieving and storing data, also optimised the geo-spatial queries for faster and accurate response from the MongoDB}
          \resumeItemListEnd
          \vspace{-13pt}
          
    \resumeProjectHeading
          {\textbf{Clickster} $|$ \emph{React, Node.js, Socket.io, Express}}{May 2022}
          \resumeItemListStart
            \resumeItem{Created an highly customised browser based multiplayer game using web sockets, was able to handle 6 concurrent games played simultaneously on node server serving the clients.}
            \resumeItem{Dockerized the application for easier deployment and testing purposes, implemented proper react toastifier for the better user experience}
          \resumeItemListEnd 
          \vspace{-13pt}
    
    \resumeProjectHeading
          {\textbf{Trano} $|$ \emph{Python, Django, Celery}}{March 2022}
          \resumeItemListStart
            \resumeItem{Developed a online ticket checking framework which reallocates the tickets if the person has not boarded the train.}
            \resumeItem{Designed and implemented point based ticket reallocation mechanism for giving priorities based upon gender, age, distance, relative distance of the destination, implemented non-blocking background tasks to reallocate the seats for the passengers.}
          \resumeItemListEnd
          \vspace{-13pt}
    
    \resumeProjectHeading
          {\textbf{Brezita} $|$ \emph{Flask, Tensorflow, Colab}}{November 2021}
          \resumeItemListStart
            \resumeItem{Created an semi-automated captcha cracker tool using Convolutional Neural Network with a decent accuracy of 88\%.}
            \resumeItem{Deployed the captcha detecting model to flask server and created a API to serve the same model for different applications.}
          \resumeItemListEnd 
          \vspace{-13pt}

    \resumeProjectHeading
          {\textbf{Caber} $|$ \emph{Php, MySql, Bootstrap, Jquery}}{April 2020}
          \resumeItemListStart
            \resumeItem{Implemenated a Webapplication that can cluster the users on the basis of date of travel and location, so they can easily cab a pool, and get a good company on the way}
            \resumeItem{Processed user inputted information in the back-end of the app to return a list of people and their basic information to contact for cab pooling.}
          \resumeItemListEnd 
          \vspace{-13pt}
          
    \resumeProjectHeading
          {\textbf{Insta-Fier} $|$ \emph{Python, Selenium}}{May 2020}
          \resumeItemListStart
            \resumeItem{Python Script using Selenium that automates the list of all the new messages and person who shared their posts which is automated using a bot.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}

% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-4pt, parsep=3pt]
%                 \item Data Structures
%                 \item Software Engineering
%                 \item Algorithms Analysis
%                 \item Database Management
%                 \item Operating System
%                 \item Internet Technology
%                 \item Compiler Design
%                 \item Computer Architecture
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     %\resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C, HTML/CSS, JavaScript, TypeScript, SQL} \\
     \textbf{Developer Tools}{: VS Code, Digital Ocean, } \\
     \textbf{Technologies/Frameworks}{: Linux, GitHub, Docker, React, Django} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{CYSCOM VITC}{November 2021 -- Present}{General Secretary}{Vellore Institute of Technology}
            \resumeItemListStart
                \resumeItem{Led a student chapter with 100+ active members to work towards goals that improve and promote the cyber security awerness and knowledge to prevent any security attacks.}
                \resumeItem{Managed national level hackathon \emph{Tetraflip} which had gathered over 500+ participants from all over the india.}
                \resumeItem{Organised including planning, operations, hospitality and overall coordination, have organised 6 events (in both online and offline mode)  with almost 100+ active participants in all the event.}
            \resumeItemListEnd

        \resumeSubheading{Dramatics Club of VIT Chennai}{November 2021 -- Present}{Performer  | Co-writer}{Vellore Institute of Technology}
            \resumeItemListStart
                \resumeItem{Secured \nth{1} position in overall best play category at Drama League an annual stage play fest organised by Dramatics Club of VIT Chennai.}
                \resumeItem{Bagged \nth{3} runner up position in overall best act category at RVCE, Banglore}
            \resumeItemListEnd
        
        \resumeSubheading{Technovation}{Summer 2021}{Mentor}{Vellore Institute of Technology}
            \resumeItemListStart
                \resumeItem{Mentored a group of 3 high school student in for a international level hackathon.}
                \resumeItem{Our team was the only team selected from the Chennai Region}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}
